\begin{thebibliography}{99}


\bibitem{SmithAbel}
J. O. Smith and J. S. Abel, ``Closed-form least-squares source location estimation from range-difference measurements,'' {\em IEEE Trans. on Acoustic, Speech Signal Proc.}, vol. 12, pp. 1661--1669, Dec. 1987.

\bibitem{ShcauRob}
H. Schau and A. Robinson, ``Passive source localization employing intersecting spherical surfaces from time-of-arrival differences,'' {\em IEEE Trans. on Acoustic, Speech Signal Proc.}, vol. ASSP--35, pp. 1223--1225, Aug. 1987.

\bibitem{Yao}
K. Yao, R. Hudson, C. Reed, D. Chen, and F. Lorenzelli, ``Blind beamforming on a randomly distributed sensor array system,'' {\em IEEE J. Select. Areas Commun.}, vol. 16, pp. 1555-1567, Oct. 1998.

\bibitem{Sprito}
 M. A. Sprito, ``On the accuracy of cellular mobile station location estimation,'' {\em IEEE Trans. on Veh. Technol.}, vol. 50, pp. 674-685, May 2001.

\bibitem{Huang}
 Y. Huang, J. Benesty, G. W. Elko, and R. M. Mersereau, ``Realtime passive source localization: A practical linear correction least-squares approach,'' {\em IEEE Trans. on Speech Audio Proc.}, vol. 9, no. 8, pp. 943-956, Nov. 2002.


\bibitem{CheungChan}
 K. W. Cheung, H. C. So, W. K. Ma, and Y. T. Chan, ``Least squares algorithms for time-of-arrival-based mobile location,'' {\em IEEE Trans. on Signal Proc.}, vol. 52, no. 4, pp. 1121--1228, Apr. 2004.

\bibitem{LiHu}
D. Li and H. Hu, ``Energy-Based Collaborative Source Localization Using Acoustic Microsensor Array,'' in {\em EURASIP Journal on Applied Signal Proc.}, vol. 4, 321--337, 2003.
%D. Li and H. Hu, ``Least square solutions of energy based acoustic source localization problems,'' in {\em Proc. ICPPW}, 2004.

\bibitem{ShengHu}
X. Sheng and Y.-H. Hu, ``ML Multiple-source localization using acoustic energy measurements with wireless sensor networks,'' {\em IEEE Trans. on Signal Proc.}, vol. 53, no.1, pp. 44--53, Jan. 2005.

\bibitem{Saric}
Z. M. Saric, D. D. Kukolj, and N. D. Teslic, ``Acoustic source localization in wireless sensor network'', {\em Circuits Syst Signal Proc.}, vol. 29, pp. 837--856, 2010.

\bibitem{LuWuYan}
L.Lu, H.-C. Wu, K.Yan, and S.Iyengar, ``Robust expectation maximization algorithm for multiple wideband acoustic source localization  in  the  presence  of  nonuniform  noise  variances,'' {\em IEEE Sensors J.}, vol. 11, no. 3, pp. 536--544, Mar. 2011.

\bibitem{Cheung}
K.W. Cheung, W.K. Ma, and H.C. So, ``Accurate approximation algorithm for TOA-based maximum-likelihood mobile location using semidefinite programming,'' in {\em Proc. ICASSP}, vol. 2, pp. 145--148, 2004.

\bibitem{Sayed}
A. H. Sayed, A. Tarighat, and N. Khajehnouri, ``Network-based wireless location,'' {\em IEEE Signal Pro. Mag.}, vol. 22, no. 4, pp. 24--40, July 2005.

\bibitem{Chan}
 Y. T. Chan, H. Y. C. Hang, and P. C. Ching, ``Exact and approximate maximum likelihood localization algorithms,'' {\em IEEE Trans. on Veh. Technol.}, vol. 55, no. 1, pp. 10--16, Jan. 2006.

\bibitem{StLi}
P. Stoica and J. Li, ``Source localization from range-difference measurements,'' {\em IEEE Signal Proc. Mag.}, vol. 23, pp. 63--65,69, Nov. 2006.

\bibitem{BeckStLi}
A. Beck, P. Stoica and J. Li,  ``Exact and approximate solutions of source localization problems,'' {\em IEEE Trans. on Signal Proc.}, vol. 56, no. 5, pp. 1770--1777, May 2008.

\bibitem{BeckTeCh}
A. Beck, M. Teboulle, and Z. Chikishev, ``Iterative minimization schemes for solving the single source localization problem,''  {\em SIAM J. Optim.}, vol. 19, no. 3, pp. 1397--1416, Nov. 2008.

\bibitem{Daub}
I. Daubechies, R. DeVore, M. Fornasier, and C. S. G\"unt\"urk, ``Iteratively reweighted least squares minimization for sparse recovery,'' {\em Comm. Pure Appl. Math.}, vol. 63, pp. 1--38, 2010.

\bibitem{BeckGPS}
A. Beck, and D. Pan, ``On the solution of the GPS localization and circle fitting problems,''  {\em SIAM J. Optim.}, vol. 22, no. 1, pp. 108--134, Jan. 2012.

\bibitem{Beck15}
A. Beck, ``On the convergence of alternating minimization for convex programming with applications to iteratively re-weighted least squares and decomposition schemes,''  {\em SIAM J. Optim.}, vol. 25, no. 1, pp. 185-209, Jan. 2015.

\bibitem{More}
J.J. More, ``Generalizations of the trust region subproblem,'' {\em Optim. Methods Softw.}, vol. 2, pp. 189--209, 1993.

\bibitem{FortinWol}
C. Fortin and H. Wolkowicz, ``The trust region subproblem and semidefinite programming,'' {\em Optim. Methods Softw.}, vol. 19, no.1, pp. 41--67, 2004.

\bibitem{RReg}
D.P. O'Leary, ``Robust regression computation using iteratively reweighted least squares,'' {\em SIAM J. Matrix Anal. Appl.}, vol. 11, no. 3, pp. 466--480, 1990.

\bibitem{GIRLS}
N. Bissantz, L. D\"umbgen, A. Munk, and B.  Stratmann, ``Convergence analysis of generalized iteratively reweighted least squares algorithms on convex function spaces,'' {\em SIAM J. Optim.}, vol. 19, no. 4, pp 1828--1845, 2009.


%\bibitem{Weiz}
%E. Weiszfeld, ``On the point for which the sum of the distances to n given points is minimum,'' {\em Ann. Oper. Res.,}, vol. 167, pp. 7--41, 2009; translated from the French original [Tohoku Math. J., 43 (1937), pp. 355--386] and annotated by F. Plastria.

\bibitem{classMDS}
K. W. Cheung and H. C. So, ``A multidimensional scaling framework for mobile location using time-of-arrival measurements,'' {\em IEEE Trans. on Signal Proc.}, vol. 53, no. 2, pp. 460--470, Feb. 2005.

\bibitem{fastMDS}
S. Qin, Q. Wan, and L.-F. Duan, ``Fast and efficient multidimentional scaling algorithm for mobile positioning,'' {\em IET Signal Processing}, vol. 6, no. 9, pp. 857--861, March 2012.

\bibitem{dwMDS}
J.A. Costa, N. Patwari, and A. O. Hero, ``Distributed weighted-multidimentional scaling for node localization in sensor networks,''ACD Trans. Sens. Netw., vol. 2, no. 1, pp. 39--64, 2006. 

\bibitem{genMDS}
H.C. So and F.K.W. Chan, ``Generalized Subspace Approach for Mobile Positioning With Time-of-Arrival Measurements,'' {\em IEEE Trans. on Signal Proc.}, vol. 55, no. 10, pp. 5103--5107, October 2007.

\bibitem{LiuSurvey}
H. Liu, H. Darabi, P. B, and J. Liu, ``Survey of Wireless Indoor Positioning Techniques and Systems,'' {\em IEEE Trans. on Systems, Man and Cybernetics. Part C: Applications and Revies}, vol. 37, no. 6, pp. 1067--1080, Nov. 2007.

\bibitem{LiuHuPan}
Y. Liu, Y.H. Hu, and Q. Pan, ``Distributed, Robust Acoustic Source Localization in a Wireless Sensor Network,'' {\em IEEE Trans. on Signal Proc.}, vol. 60, no. 8, pp. 4350--4359, Aug. 2012.

\bibitem{KimLeJe}
W. Kim, J. Lee, and G. Jee, ``The interior-point method for an optimal treatment of bias in trilateration location,'' {\em IEEE Trans. Veh. Technol.}, vol. 55, no. 4, pp. 1291--1301, Jul. 2006.

\bibitem{SMAC}
T. Qiao, S. Redfield, A. Abbasi, Z. Su, and H. Liu, ``Robust coarse position estimation for TDOA localization,'' {\em IEEE Wireless Commun. Lett.}, vol. 2, no. 6, pp. 623--626, Dec. 2013.

\bibitem{Yu}
A. L. Yuille and A. Rangarajan, ``The concave-convex procedure,' {\em Neural Computation}, vol. 15, no. 4, pp. 915--936, 2003.

\bibitem{LBoyd}
T. Lipp and S. Boyd, ``Variations and extensions of the convex-concave procedure,'' {\em Research Report}, Stanford University, Aug. 2014.

\bibitem{CCPConv}
G. R. Lanckreit and B. K. Sriperumbudur, ``On the convergence of the concave-convex procedure,'' in  {\em Advances in Neural Information Proc. Systems}, pp. 1759--1767, 2009.

\bibitem{CCPGlob}
Y. Kang, Z. Zhang, and W.-J. Li, ``On the global convergence of majorization minimization algorithms for nonconvex optimization problems,'' in {\em arXiv:
1504.07791v2}, 2015.

\bibitem{clock}
M. R. Gholami, S. Gezici, and E. G. Str\"om, ``TW-TOA based positioning in the presence of clock imperfections,'' {\em  Digital Signal Processing}, vol. 59, pp. 19--30, 2016.

\bibitem{UWB}
M. R. Gholami, E. G. Str\"om, F. Sottile, D. Dardari, A. Conti, S. Gezici, M. Rydstr\"om, and M. A. Spirito, ``Static positioning using UWB range measurements,'' in {\em Future Network and Mobile Summit Conference Proceedings}, %Florence,  
pp. 1--10, 2010.

\bibitem{DarWinUWB}
D. Dardari, A.Conti, U.J. Ferner, A. Giorgetti, and M.Z. Win, ``Ranging with ultrawide bandwidth signals in multipath environments,'' {\em Proceedings of the IEEE}, vol. 97, pp. 427--450, 2009.

\bibitem{RydstromUWB}
M. R. Gholami, E. G. Str\"om, and M. Rydstr\"om, ``Indoor sensor node positioning using UWB range measurements,'' in {\em 17th European Signal Processing Conference (Eusipco)}, pp. 1943--1947, 2009.

\bibitem{VBoyd}
L. Vandenberghe and S. Boyd, ``Semidefinite programming,'' {\em SIAM Rev.}, vol. 38, no. 1, pp. 40--95, Mar. 1996.

\bibitem{Har}
P. Hartman, ``On functions representable as a difference of convex functions,'' {\em Pacific Journal of Math}, vol. 9, no. 3, pp. 707--713, 1959.

\bibitem{AntonLu}
A. Antoniou and W.-S. Lu, {\em Practical Optimization: Algorithms and Engineering Applications}, Springer, New-York, 2007.

\bibitem{Nes}
Y. Nesterov, {\em Introductory Lectures on Convex Optimization}, Kluwer Academic Publishers, Boston, 2004.

\bibitem{GeoLoc}
C. Gentile, N. Alsindi, R. Raulefs, and C. Teolis, {\em Geolocation Techniques: Principles and Applications}, Springer, New-York, 2013.

\bibitem{LocAlg}
G. Mao and B. Fidan, {\em Localization Algorithms and Strategies for Wireless Sensor Networks: Monitoring and Surveillance Techniques for Target Tracking},  Hershey, PA: IGI Global, New-York, 2009.

\bibitem{cvx}
CVX Research, http://cvx.com/cvx, August 2012.

\bibitem{matlab}
The Mathworks Inc., http://mathworks.com, 2015.

\bibitem{IRWSg}
``Iterative re-weighting''

\bibitem{PCCP}
``Penalty Convex-Concave Procedure of Source Localization Problem,''

\end{thebibliography}