\newpage
\TOCadd{Acknowledgements}

\begin{center}
ACKNOWLEDGEMENTS
\end{center}

Most importanly, I am greatly indebted to Dr. Lu for the opportunities he has given me. Without his guidance, encouragement, support, dedicated time and patience I would not have achieved much success in my studies. I thank the Universe for granting me a chance to work under the supervision of Dr. Lu. 

I would like to thank Dr. Yang Shi for agreeing to serve as my external examiner.  I  am also grateful to Dr. Yang Shi and Dr. Pan Agathoklis for their valuable feedback that helped  to improve this work. I would like to thank the staff  members in the Department of Electrical and Computer Engineering for providing assistance throughout my graduate studies. 

I am grateful to my friends,  Alex, Ashley, Feng, Ioanna, David, Weiheng,  Farida, and Aridiane, 
 %and colleagues who I met in Victoria,
 for cheerful moments we shared together. They believed in the success of my  pursuits even when it seemed unreachable to me. I feel fortunate that they are part of my life. 

My deepest gratitude belongs to my mother for her patience, unconditional love and trust in my judgement. % when taking risks and making decisions. I owe to her being the person I am today. 
%I owe to her support the courage to my own way. % quit a promising career and follow my dreams in exchange.


%
%\noindent I would like to thank:
%\begin{description}
%\item[my cat, Star Trek, and the weather,]
%	for supporting me in the low moments.
%\item[Supervisor Main,]
%	for  mentoring, support, encouragement, and patience.
%\item[Grant Organization Name,]
%	for funding me with a Scholarship.
%\end{description}
%
%\begin{flushright}
%\textit{I believe I know the only cure, which is to make
%one's centre of life inside of one's self, not
%selfishly or excludingly, but with a kind of
%unassailable serenity-to decorate one's inner house
%so richly that one is content there, glad to welcome
%any one who wants to come and stay, but happy all
%the same in the hours when one is inevitably alone.}
%\\
%Edith Wharton \\
%\end{flushright}
